Comment: Inferring Trade Costs from Trade Booms and Trade Busts

### 2017-09-15 Paper/Manuscript.tex
réglé un doute

\documentclass{article}
\usepackage{authblk}
\usepackage{natbib}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[pdftex]{graphicx}  
%Langue utilisée
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\emergencystretch=8em
\usepackage[margin=1in]{geometry}
\usepackage{booktabs}
\usepackage{tabularx}

@@

\end{tabularx}
\caption{Decomposition of the growth in international trade
(logarithms) with \textit{ad hoc} averages and a microfounded
aggregation method. First wave of globalization,
1870-1913.  \emph{JMN 2011} refers to the averaging over dyads,
\emph{JMN by country} by country refers to the averaging over
trading partners for one country, \emph{our methodl}
refers to the aggregation method we offer.}\label{glob1}
\end{table}

@@

\end{tabularx}
\caption{Decomposition of the growth in international trade
(logarithms) with \textit{ad hoc} averages and a microfounded
aggregation method. Second wave of globalization, 1950-2000.
\emph{JMN 2011} refers to the averaging over dyads,
\emph{JMN by country} by country refers to the averaging over
trading partners for one country, \emph{our methodl}
refers to the aggregation method we offer.}\label{glob2}
\end{table}

@@

Insofar as a measure of trade costs is defined residually as everything that explains differences between domestic and international trade flows, it is bound to reword the information contained in an openness ratio.

>>>>

\documentclass{article}
\usepackage{authblk}
\usepackage{natbib}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[pdftex]{graphicx}  
%Langue utilisée
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\emergencystretch=8em
\usepackage[margin=1in]{geometry}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{tablefootnote}

@@

\end{tabularx}

\caption{Decomposition of the growth in international trade
(logarithms) with \textit{ad hoc} averages and a microfounded
aggregation method. First wave of globalization,
1870-1913.  \emph{JMN 2011} refers to the averaging over dyads,
\emph{JMN by country} by country refers to the averaging over
trading partners for one country, \emph{our methodl}
refers to the aggregation method we offer. \hspace{\linewidth}
\textbf{Note:} The contribution of output growth is constant for all countries in our method because it is measured as the growth of total world output}\label{glob1}
\end{table}

@@

\end{tabularx}
\caption{Decomposition of the growth in international trade
(logarithms) with \textit{ad hoc} averages and a microfounded
aggregation method. Second wave of globalization, 1950-2000.
\emph{JMN 2011} refers to the averaging over dyads,
\emph{JMN by country} by country refers to the averaging over
trading partners for one country, \emph{our methodl}
refers to the aggregation method we offer.\hspace{\linewidth}
\textbf{Note:} The contribution of output growth is constant for all countries in our method because it is measured as the growth of total world output}\label{glob2}
\end{table}

@@
